New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2022-07-13 paper/paper.Rmd
Sentence about preprocessing and reference to remove the blindfold paper added.

To illustrate the usefulness of the manual controls we use the 4D penguins data [@penguins]. We will show how classification boundaries can be explored and better understood on projections and slices through 4D space. Figure \ref{fig:penguins-scatmat} shows a scatterplot matrix of this data. There are four variables (`bl = bill_length_mm, bd = bill_depth_mm, fl = flipper_length_mm, bm = body_mass_g`) measuring the size of the penguins from three species (Adelie, Chinstrap and Gentoo). The scatterplot matrix shows that the three species appear to be likely separable, and that at least the Gentoo can be distinguished from the other two species when `bd` is paired with `fl` or `bm`. The steps for exploring boundaries in this example are as follows:

@@

We use the `classifly` package [@classifly] to generate predictions across the 4D cube spanned by the data, with two classification models: linear discriminant analysis (LDA) and random forest (RF).

>>>>

To illustrate the usefulness of the manual controls we use the 4D penguins data [@penguins] and look at classification models following @sam11271. We will show how classification boundaries can be explored and better understood on projections and slices through 4D space. Figure \ref{fig:penguins-scatmat} shows a scatterplot matrix of this data. There are four variables (`bl = bill_length_mm, bd = bill_depth_mm, fl = flipper_length_mm, bm = body_mass_g`) measuring the size of the penguins from three species (Adelie, Chinstrap and Gentoo). The scatterplot matrix shows that the three species appear to be likely separable, and that at least the Gentoo can be distinguished from the other two species when `bd` is paired with `fl` or `bm`. The steps for exploring boundaries in this example are as follows:

@@

We use the `classifly` package [@classifly] to generate predictions across the 4D cube spanned by the data, with two classification models: linear discriminant analysis (LDA) and random forest (RF). Both the data and the model points in the grid are centered and scaled (standard deviation $= 1$).

### 2022-07-13 paper/paper.tex
Sentence about preprocessing and reference to remove the blindfold paper added.

To illustrate the usefulness of the manual controls we use the 4D
penguins data \citep{penguins}. We will show how classification
boundaries can be explored and better understood on projections and
slices through 4D space. Figure \ref{fig:penguins-scatmat} shows a
scatterplot matrix of this data. There are four variables
(\texttt{bl\ =\ bill\_length\_mm,\ bd\ =\ bill\_depth\_mm,\ fl\ =\ flipper\_length\_mm,\ bm\ =\ body\_mass\_g})
measuring the size of the penguins from three species (Adelie, Chinstrap
and Gentoo). The scatterplot matrix shows that the three species appear
to be likely separable, and that at least the Gentoo can be
distinguished from the other two species when \texttt{bd} is paired with
\texttt{fl} or \texttt{bm}. The steps for exploring boundaries in this
example are as follows:

@@

We use the \texttt{classifly} package \citep{classifly} to generate
predictions across the 4D cube spanned by the data, with two
classification models: linear discriminant analysis (LDA) and random
forest (RF).

>>>>

To illustrate the usefulness of the manual controls we use the 4D
penguins data \citep{penguins} and look at classification models
following \citet{sam11271}. We will show how classification boundaries
can be explored and better understood on projections and slices through
4D space. Figure \ref{fig:penguins-scatmat} shows a scatterplot matrix
of this data. There are four variables
(\texttt{bl\ =\ bill\_length\_mm,\ bd\ =\ bill\_depth\_mm,\ fl\ =\ flipper\_length\_mm,\ bm\ =\ body\_mass\_g})
measuring the size of the penguins from three species (Adelie, Chinstrap
and Gentoo). The scatterplot matrix shows that the three species appear
to be likely separable, and that at least the Gentoo can be
distinguished from the other two species when \texttt{bd} is paired with
\texttt{fl} or \texttt{bm}. The steps for exploring boundaries in this
example are as follows:

@@

We use the \texttt{classifly} package \citep{classifly} to generate
predictions across the 4D cube spanned by the data, with two
classification models: linear discriminant analysis (LDA) and random
forest (RF). Both the data and the model points in the grid are centered
and scaled (standard deviation \(= 1\)).
